Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-03-08 rmd/suppl_info.Rmd
update: si

---
output:
  pdf_document:
    toc: true
    latex_engine: xelatex
    includes:
      before_body: title.tex
mainfont: Times New Roman
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
fontsize: 11pt
header-includes:
  \pagenumbering{gobble}
  \usepackage{amsmath}
---

@@

```{=tex}
\newpage
\pagenumbering{arabic}
```
# Supplementary text

@@

@@

## Add

- total carrying capacity
- mean distance

>>>>

---
output:
  pdf_document:
    toc: true
    latex_engine: xelatex
    includes:
      before_body: title.tex
mainfont: Times New Roman
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
fontsize: 11pt
header-includes:
  - \usepackage{amsmath, fancyhdr, caption, booktabs}
  - \pagestyle{fancy}
  - \renewcommand{\headrulewidth}{0pt}
  - \pagenumbering{gobble}
---

@@

```{=tex}
\newpage
\pagestyle{fancy}
\fancyhead[L]{Pomeranz et al.}
\fancyhead[C]{}
\renewcommand{\headrulewidth}{0.5pt}
\pagenumbering{arabic}
\def\figurename{Figure S\hspace{-.4ex}}
\def\tablename{Table S\hspace{-.4ex}}
```
# Supplementary text

@@

# Tables

```{r}
source(here::here("code/table_param.R"))

kable(df_value,
      escape = FALSE,
      booktabs = TRUE,
      caption = "Parameter values used in the main simulation and one-patch simulation") %>% 
  kableExtra::kable_styling(latex_options = 'HOLD_position')
```

@@

```{r fig10, fig.cap="Ecosystem size and complexity dictate total carrying capacity (= $\\sum_x K_x$) and mean distance between a given pair of habitat patches within a network."}
knitr::include_graphics(here::here("figure/figure_si_k_distance.pdf"))
```
